Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-07 ms/main.tex
Add figure 5

>>>>

%%% Figure: invasion
\begin{figure}[b]
  \centering
   \includegraphics[scale=0.4]{Frequency_of_invadors.eps}
    ~
    \includegraphics[scale=0.4]{Frequency_of_cooperation_after_invasion.eps}\\ 
  \caption{
  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
  \textbf{(a)} describes the frequency of the invadors. 
  \textbf{(b)} describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency $\hat{p}_2^*$ which described by the black dashed line. 
  $\hat{p}_2^*$ is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
  }
  \label{fig:invasion}
\end{figure}
